\section{Introduction}

%% [ ] Talk about latest in the field of handwriting recognition
%% [x] Gather some statistics about the Indexing program of the LDS Church
%% [x] Add and refine a humorous introduction
%% [x] Talk about why this problem is interesting


With the new movie release of Star Wars we thought about the genius of C-3PO.  This wonderous robot who was recognized as a God to little teddy bear creatures is fluent in over six million forms of communication.  For our project we wished to create a universal translator such as C-3PO however we were encourage to focus on creating a universal translator of a single handwritten letter "m" or "f"; which represents the gender of a indivudal in Alabama in 1836.

Now for the real project.  The Church of Jesus Christ of Latter-Day Saints does extensive work with digitizing census records into a digital format.  This is done manually and all over the world.  In 2015, 330 million records were manually indexed through the indexing program of the Church of Jesus Christ of Latter-Day Saints (LDS Church) \cite{web:indexingStats}.  Today alone, 88,000 records were indexed by individuals all around the world \cite{web:indexingStats}.  There are millions of records waiting to be indexed so that members and non-members alike can connect the dots in compiling their family history.  There is so much information stored in handwritten form.  We currently rely on people to descipher what is written.

We decided to try our hand at using machine learning to automate indexing of historical documents.  In the general case, handwriting recognition is extremely difficult.  There can be wild variations in handwriting style, as well as corrections and mistakes.  To limit the scope of our project, we limited the task to recognizing a handwritten M or F in the gender field of an old census record.

Using data we obtained from the LDS Church, we processed, cleaned, and ran various learning algorithms.  This included classifiers we learned from class.  We also explored using Deep Learning.  Of these methods, Deep Learning proved the most effective, however pretty strong results came from linear classifiers.  We learned that success in Machine Learning has as much to do with activities other than machine learning algorithms, such as gathering, cleaning, and preprocessing data.

